Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-30 ba_resubmit_template_files/main.tex
fixd number

	We link records using sex, location, and day, month, and year of birth using the criteria shown in Table \ref{Tab:nltcs-comparisons}. Storing $\gamma$ constructed through three comparison scores for each of $20485 (17466) \approx$ 400 million record pairs would require approximately 8 GB of memory. Standard settings on a 16 GB personal computer do not allow storage of an object of this size, and thus \texttt{BRL} is unable to perform this linkage task on such a machine. However, through the method described in Section \ref{scaling},  we perform 30 smaller comparison tasks, using $t_A = 1$ and $t_B = 30$. We conduct linkage with all record indices recorded and also with SEI using $S=10$, and obtain identical results. The hashed $\tilde{\gamma}$ without SEI is about 2.2 GB, and with SEI, it is about 760 MB. Constructing the comparisons sequentially took approximately 40 minutes, which could be reduced considerably through parallel computing.

>>>>

	We link records using sex, location, and day, month, and year of birth using the criteria shown in Table \ref{Tab:nltcs-comparisons}. Storing $\gamma$ constructed through three comparison scores for each of the approximately 400 million record pairs would require around 8 GB of memory. Standard settings on a 16 GB personal computer do not allow storage of an object of this size, and thus \texttt{BRL} is unable to perform this linkage task on such a machine. However, through the method described in Section \ref{scaling},  we perform 30 smaller comparison tasks, using $t_A = 1$ and $t_B = 30$. We conduct linkage with all record indices recorded and also with SEI using $S=10$, and obtain identical results. The hashed $\tilde{\gamma}$ without SEI is about 2.2 GB, and with SEI, it is about 760 MB. Constructing the comparisons sequentially took approximately 40 minutes, which could be reduced considerably through parallel computing.
